Theories of deliberated choice

### 2023-10-09 simple.tex
Branched while forgetting crashed version

While numerous articles have discussed the concept of deliberation in the last decades, it remains unsettled, to the best of my knowledge, how to observe a deliberated judgment in a systematic and reproducible fashion. There is a need to define this concept sufficiently precisely that, first, it is clear what counts as a deliberated judgment (i.e., when “sufficient” \citep{meinard_justification_2020} or “correct” deliberation has happened); and second, it is clear which part of the claim is empirical and which part stems from an unfalsifiable conception of what “deliberated” means. This permits to study deliberated judgments empirically, meaning here that disagreements about someone’s deliberated judgment in a given context can be solved, at least in principle, by an empirical experiment, provided the very conception of what constitutes a deliberated judgment is shared. This article is interested in defining the concept of deliberated judgement of a subject and show how one can study it in an empirical manner. The “classical” counterpart of deliberated judgments,, that does not involve confrontation with arguments, will henceforth be called the natural judgment. As we deal with choice acts, we will also name the concept “deliberated choice”, as opposed to “natural choice”.

@@

We can observe set $O$ that forms a function $f(i) = \set{\alpha \ileadsto \phi, \alpha' \ileadsto ¬\phi, …}$, with $\alpha \subset \alpha \subset …$ and with finite $O$.
Our second condition is that $¬C \implies \exists O \suchthat O \implies ¬C$.
For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \allleadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \allleadsto ¬\phi$, then $O$ implies $¬C$.
As another example, $C$ being $\exists \alpha \suchthat \alpha \ileadsto \phi$ is unfalsifiable, as its negation is $\forall \alpha: \alpha \nileadsto \phi$, which requires infinite $O$.

@@

Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq P^{I × \allhist}$.
When writing $C$ as a formula, it is intended to mean the set $\set{{\allleadstog} \in P^{I × \allhist} \suchthat C({\allleadstog})}$.

Given a pair $(I, \allargs)$, a general observation $O$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in O: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
Let $S_O = \set{{\allleadstog} \in P^{I × \allhist} \suchthat O \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.

A claim $C$ is falsifiable iff $\exists O \suchthat O \implies ¬C$, by which I mean $S_O \cap C = \emptyset$.
\begin{example}
	$(\ar) \ileadstog \phi \lor (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
%	Its negation is $\forall k: (\ar^k) \nileadsto \phi$.
%	The claim represents the set $\set{{\allleadsto} \in P^{I × \allhist} \suchthat (\ar) \ileadsto \phi \lor  (\ar, \ar) \ileadsto \phi \lor …}$.
	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$. Pick any $\allleadstog$ such that $O \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}
	$(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
	Given any $O$, it may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any $\allleadstog$ such that $O \subset {\allleadstog} \land t \in {\allleadstog}$. We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}[Fals. but shouldn’t]
	\label{ex:fbs}
	$\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is falsifiable.
	Consider $O = \set{(j, \hist, ¬\phi)}$.
\end{example}
\begin{example}
	$\forall i: \ar \ileadstostg \phi$ is falsifiable.
	Consider any $i \in I$ and $O = \set{(i, (\ar), ¬\phi)}$.
\end{example}
\Cref{ex:fbs} shows that this definition of falsifiability is wrong.

We now say that $C$ is \emph{falsifiable} iff $\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists O \subseteq {\allleadstog} \suchthat O \implies ¬C$, meaning that
$\forall {\allleadstog} \notin C: \exists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset$.
\begin{example}
	$(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
	Given any $O$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in O} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in O$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $O \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}
	\label{ex:unfals}
	$(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
	Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
	Consider any $O \subseteq {\allleadstog}$ and let us prove that $S_O \cap C ≠ \emptyset$.
	By definition of a general observation, $O$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $O$, pick any ${\allleadstog'}$ such that $O \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_O \cap C ≠ \emptyset$.
\end{example}
\begin{example}
	$\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
	Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
	\Cref{ex:unfals} concludes.
\end{example}
\begin{example}
	Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
	Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $O = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}
\begin{example}
	Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
	Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $O \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_O \cap C ≠ \emptyset$.
\end{example}

Given an exposure protocol $\allleadsto$, we say that a claim $C$ \emph{holds} iff $C \ni {\allleadsto}$.

The following theorem verifies that when $C$ holds, it will not be falsified ex post (though it may be (a priori) falsifiable).
\begin{theorem}
	\label{th:ex-post}
	$\forall C \ni {\allleadsto}: \nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset$.
\end{theorem}
\begin{proof}
	We have, $\forall C \suchthat C \ni {\allleadsto}, \forall O \subseteq {\allleadsto}$: $O \subseteq {\allleadsto} \in C$, equivalently, ${\allleadsto} \in S_O \cap C$, thus $S_O \cap C ≠ \emptyset$.
\end{proof}
Therefore, falsifiability guarantees that a claim holds if, and only if, it is not a posteriori falsifiable. (TODO syntactically fals VS empirically fals.)
\begin{theorem}
	\label{th:holdsiff}
	For all falsifiable $C$: ${\allleadsto} \in C$ iff $\nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset$.
\end{theorem}
\begin{proof}
	Consider any falsifiable $C$.
	By definition of falsifiability, $\forall {\allleadstog}: \nexists O \subseteq {\allleadstog} \suchthat S_O \cap C = \emptyset \implies {\allleadstog} \in C$.
	In particular,
	$\nexists O \subseteq {\allleadsto} \suchthat S_O \cap C = \emptyset \implies {\allleadsto} \in C$.
	The reverse implication is proven by \cref{th:ex-post}.
\end{proof}

@@

Given $\histk \in \allhist$ and $\ar_l \in \allargs$, let $(\histk, …, \ar_l, ?)$ denote the set 
$\set{\histl \suchthat \histk \subset \histl \land \ar_l \in \histlend}$.
Given $\hist \in \allhist$, ${\ileadstog}$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set 
$\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
Given $\ar_k, \ar_l \in \allargs$, let 
$(…, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set 
$\cup_{\hist \in \allhist} (\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) = 
\set{\histl \suchthat \exists \hist, \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend} = 
\set{\histl \suchthat \exists \histk \suchthat \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
Given ${\ileadstog}$, $p \in P$, $s \in \allargs$ and $S \subseteq \allargs$, note that $s \in \ileadstoinvg(p)$ stand for $s \ileadstog p$ and $S \subseteq \ileadstoinvg(p)$ stand for $\forall s \in S: s \ileadstog p$.

@@

\begin{theorem}
	Given any $p \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$: 
	\begin{multline}
		\label{eq:cl}
		\forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
		\forall \hist \in (…, \ar_1, ?) \cap \nileadstoinvg(p): \\
		(\hist, …, \ar_2, ?) \subseteq \ileadstoinvg(p).
	\end{multline}
	Assume that ${\allleadsto} \in C$. Then 
	$\exists i \in I \suchthat [\ar_k \nileadstost p \land \ar_l \nileadstost p]$ 
	is equivalent to: 
	\begin{multline}
		\label{eq:cln}
		\exists i \in I \suchthat \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l}:\\
		\exists \hist \in (…, \ar_1, ?) \cap \nileadstoinv(p) \suchthat
		(\hist, …, \ar_2, ?) \subseteq \ileadstoinv(p).
	\end{multline}
\end{theorem}
\begin{proof}
	$\ar_k \nileadstost p$ iff $\exists \hist \suchthat \ar_k \in \histend \land \hist \nileadsto p$.
\end{proof}
\begin{remark}
	Idea.
	That consequence is unfalsifiable so we cannot include anything like this in $C$ (only something stronger, but of course a stronger statement could be false). Therefore, with no addition, we are doomed that exists some situations where no claim is suitable.
\end{remark}
\begin{theorem}
	The claim \eqref{eq:cl} and not \eqref{eq:cln}, thus, \eqref{eq:cl} and $\forall i, \ar_k \ileadstostg p \lor \ar_l \ileadstostg p$ is not falsifiable.
\end{theorem}
\begin{proof}

\end{proof}
\begin{theorem}[Informal]
		Assume that the NOT consequence holds and the claim holds.
	Prove that there is no suitable claim.
	If the claim is just the NOT cons and claim, then it is not fals.
	If the claim is weaker, it does not permit to prove that $\ar_k$ or $\ar_l$ is decisive. (BUT does it possibly prove that some arg is decisive? But it may be false.)
	If the claim is stronger, it may be false.
\end{theorem}
\begin{theorem}[Formal]
	Pick any $p \in P$ and $\ar_k ≠ \ar_l \in \allargs$ and assume that $\allleadsto$ fails \cref{eq:cln}, that is, satisfies:
	\begin{multline}
		\label{eq:answerable}
		\forall i \in I, \exists \set{\ar_1, \ar_2} \suchthat
		\set{\ar_1, \ar_2} = \set{\ar_k, \ar_l} \\ \land
		\forall \hist \in (…, \ar_1, ?) \cap \nileadstoinv(p): 
		(\hist, …, \ar_2, ?) \nsubseteq \nileadstoinv(p).
	\end{multline}
	Assume further that $\allleadsto$ satisfies \eqref{eq:cl}, thus:
	$\forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
\forall \hist \in (…, \ar_1, ?) \cap \nileadstoinv(p): (\hist, …, \ar_2, ?) \subseteq \ileadstoinv(p)$.
	Then, there is no suitable claim.
\end{theorem}
\begin{proof}
	Note that $\allleadsto$ satisfies, $\forall i \in I, \exists \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l} \land \forall \hist \in (…, \ar_1, ?): \hist \ileadsto p$; equivalently, $\ar_k \ileadstost p \lor \ar_l \ileadstost p$.

>>>>

While numerous articles have discussed the concept of deliberation in the last decades, it remains unsettled, to the best of my knowledge, how to observe a deliberated judgment in a systematic and reproducible fashion. There is a need to define this concept sufficiently precisely that, first, it is clear what counts as a deliberated judgment (i.e., when “sufficient” \citep{meinard_justification_2020} or “correct” deliberation has happened); and second, it is clear which part of the claim is empirical and which part stems from an unfalsifiable conception of what “deliberated” means. This permits to study deliberated judgments empirically, meaning here that disagreements about someone’s deliberated judgment in a given context can be solved, at least in principle, by an empirical experiment, provided the very conception of what constitutes a deliberated judgment is shared. This article is interested in defining the concept of deliberated judgement of a subject and show how one can study it in an empirical manner. The “classical” counterpart of deliberated judgments, that does not involve confrontation with arguments, will henceforth be called the natural judgment. As we deal with choice acts, we will also name the concept “deliberated choice”, as opposed to “natural choice”.

@@

We can observe set $O$ that forms a function $f(i) = \set{\alpha \ileadsto \phi, \alpha' \ileadsto ¬\phi, …}$, with $\alpha \subset \alpha \subset …$ and with finite $O$.
Our second condition is that $¬C \implies \exists θ \suchthat θ \implies ¬C$.
For example, if $C$ is $\alpha \ileadsto \phi \lor \beta \allleadsto[j] \phi$, $O$ is $\alpha \ileadsto ¬\phi \land \beta \allleadsto ¬\phi$, then $O$ implies $¬C$.
As another example, $C$ being $\exists \alpha \suchthat \alpha \ileadsto \phi$ is unfalsifiable, as its negation is $\forall \alpha: \alpha \nileadsto \phi$, which requires infinite $O$.

@@

Given a pair $(I, \allargs)$, a claim $C$ is a set of possibilities for $\allleadsto$, thus, $C \subseteq P^{I × \allhist}$.
Given a formula $\psi$, let the corresponding claim be $C_\psi = \set{{\allleadstog} \in P^{I × \allhist} \suchthat {\allleadstog} \text{ satisfies } \psi}$.
A claim is finite iff its cardinal is finite (meaning that it is compatible with a finite number of possibilities).

Given a pair $(I, \allargs)$, a general observation $θ$ is a right unique finite subset of $(I × \allhist) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
General observations are the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
Let $S_θ = \set{{\allleadstog} \in P^{I × \allhist} \suchthat θ \subseteq {\allleadstog}}$ denote the possibilities for $\allleadsto$ compatible with the observations.

\begin{definition}
  We say that $C$ is \emph{syntactically falsifiable}, or just falsifiable, iff
  %$\forall {\allleadstog} \in P^{I × \allhist}: ¬C({\allleadstog}) \implies \exists θ \subseteq {\allleadstog} \suchthat θ \implies ¬C$, meaning that
  $\forall {\allleadstog} \notin C: \exists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset$.
\end{definition}
\begin{example}
  $(\ar) \ileadstog \phi \lor  (\ar, \ar) \ileadstog \phi \lor …$ is not falsifiable.
  Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  \label{ex:unfals}
  $(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi$ is not falsifiable.
  Consider any ${\allleadstog} \notin C$, thus satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  $\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
  \Cref{ex:unfals} concludes.
\end{example}
\begin{example}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}
\begin{example}
  Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  Consider any $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_1) \ileadstog^2 p'$.
  The claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$ is unfalsifiable.

  Consider … (seems redundant).
\end{example}
\begin{remark}
  The claim “For each glass, it will not break on a monday or not break on a tuesday, whatever happens to it.” is not falsifiable. But one can make it stronger and falsify it, by giving a general theory of how glasses break, proving that it holds, and that it is not compatible with the claim. I should think about this.
\end{remark}
\begin{remark}
  To be falsifiable, I need each time I exclude some relation $R$ to also exclude a subset $Cbar$ such that some $O \subseteq R$ satisfies $S_O$ is entirely in $Cbar$.
\end{remark}
\begin{theorem}
  A claim $C$ is falsifiable iff its complement $\Cbar$ satisfies:
  $\forall {\allleadstog} \in \Cbar, \exists O \subseteq {\allleadstog} \suchthat S_O \subseteq \Cbar$, or equivalently:
  $\forall {\allleadstog} \in \Cbar, \exists O \subseteq {\allleadstog} \suchthat S_O \subseteq \Cbar$.
\end{theorem}

Let $E \subseteq I × \allhist$ denote an observable compatible set. It is downwards closed.
Let $M$ denote a maximal $E$.
Any $M$ maps each individual $i \in I$ to an increasing sequence.
Given ${\allleadsto}$, let $E_{\allleadsto} \subseteq {\allleadsto}$ denote the observable compatible sets (triples, not pairs, thus including values). These are the $E$ to which the value associated is the one given by $\allleadsto$.
Define similarly $M_{\allleadsto}$.
Let $X_C \subseteq I × \allhist × P$ denote a subset that is completable to some ${\allleadsto}$ in $C$. It is downwards closed.
Let $N_C$ denote a maximal such subset.
A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $E_{\allleadsto}$ equals some $X_C$.
A claim is not falsifiable iff $\exists {\allleadsto} \notin C \suchthat$ each $M_{\allleadsto}$ equals some $X_C$.
A claim is not falsifiable iff it is possible to pick some $M_{\allleadsto_1}$ from $C$ (that is, a mapping of each individual to an increasing sequence, together with the associated value from $\allleadsto_1$), some other $M_{\allleadsto_2}$ from $C$, and on their common entries (if any) these two relations agree (so their union is a right-unique relation), and so on for each possible mappings $M$, so as to form a complete $\allleadsto$ that is not in $C$.
A claim is falsifiable iff it is closed under the above picking operation.
Equivalently, a claim is not falsifiable iff this can be done for a given number of $M$ whose union is not an $X_C$.
We could need more than two such $M$'s, I suppose: for the theorem below, the number of such $M$'s is equal to the cardinal of the set on which they differ.
TODO what about finiteness of observables? Might fail falsifiability because only infinite obs would falsify.

Any claim containing two relations that differ only on incompatible observations is not falsifiable.
\begin{theorem}
  Any $C$ such that $\exists {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$) and the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, does not contain two elements that are simultaneously observable (meaning that no $θ$ contains more than one of these elements), is not falsifiable.
\end{theorem}
\begin{proof}
  Consider any $θ \subset {\allleadstog}$.
  If $θ$ is fully compatible with ${\allleadstog^1}$, then ${\allleadstog^1} \in S_θ \cap C ≠ \emptyset$.
  Otherwise, $θ$ contains some element $(i, \hist, {\allleadstog^2}(i, \hist))$ with ${\allleadstog^2}(i, \hist) ≠ {\allleadstog^1}(i, \hist)$. Then, ${\allleadstog^2} \in S_θ \cap C ≠ \emptyset$, for otherwise, for at least one other element $(i', \histp)$, $θ$ contains $(i', \histp, {\allleadstog^1}(i', \histp))$ with ${\allleadstog^1}(i', \histp) ≠ {\allleadstog^2}(i', \histp)$, which violates the hypothesis.
\end{proof}
The following example illustrates the need for the condition about the combination in the theorem.
\begin{example}
  Pick $i \in I$, $p ≠ p' \in P$ and $\hist, \histp \in \allhist$ with $\hist$ and $\histp$ non prefix related.
  The claim $\psi = (\hist \ileadstog p \lor \hist \ileadstog p') \land (\histp \ileadstog p \lor \histp \ileadstog p') \land (\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p)$ is falsifiable.

  Given $q, q' \in P$, let ${\allleadstog^{q, q'}}$ be defined as $\hist \ileadstog^{q, q'} q$, $\histp \ileadstog q'$ and $\forall (j, \histpp) \in (I × h) \setminus \set{(i, \hist), (i, \histp)}: \histpp \ileadstog[j] p$.
  Note that $C_\psi = \set{{\allleadstog^{p, p}}, {\allleadstog^{p, p'}}, {\allleadstog^{p', p}}, {\allleadstog^{p', p'}}}$.
\end{example}

\begin{conjecture}
  If a claim $C$ is not falsifiable, then $\exists {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$) and the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, does not contain two elements that are simultaneously observable (meaning that no $θ$ contains more than one of these elements).
\end{conjecture}
\begin{conjecture}
  If $\forall {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$), the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, contains at least two elements that are simultaneously observable (meaning that some $θ$ contains more than one of these elements), then $C$ is falsifiable.
\end{conjecture}
\begin{proof}
  We need a stronger hypothesis.
  Consider $one$ and $two$ differ on $(i, (a))$, $(i, (b))$ and $(i, (a, a))$. And some $three$ not in $C$ has $(i, (a)), (i, (a, a))$ as in $one$ and $(i, (b))$ as in $two$. Then $C$ is not falsifiable.
\end{proof}
\begin{conjecture}
  If $\forall {\allleadstog^1}, {\allleadstog^2} \in C \suchthat$ some combination of them ${\allleadstog} \notin C$ (meaning that ${\allleadstog} \subseteq {\allleadstog^1} \cup {\allleadstog^2}$), the set over which they differ, $\set{(i, \hist) \suchthat {\allleadstog^1}(i, \hist) ≠ {\allleadstog^2}(i, \hist)}$, we can find some $(i, \hist) \in {\allleadstog^1}, (j, \hist') \in {\allleadstog^2}$ obs-compatible, then $C$ is falsifiable.
\end{conjecture}
\begin{proof}
  This fails. Could have $one$, $two$, $three$, each sending everything to $p$, $¬p$ and $0$, respectively, and any combination of two of these in $C$, but no comb of three in $C$. Then $four$ a combination of the three ($i, a, p, i, b, ¬p, i, c, 0$), but $C$ not falsifiable. Actually, even if we can observe two among the three (using $i, a, p, i, aa, ¬p, i, b, 0$), we can’t falsifiy $four$.
\end{proof}

Given an exposure protocol $\allleadsto$, we say that a claim $C$ \emph{holds} iff $C \ni {\allleadsto}$.
We say that $C$ is \emph{empirically falsifiable} iff $\exists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset$.

The following theorem verifies that when $C$ holds, it is not empirically falsifiable (though it may be syntactically falsifiable).
\begin{theorem}
  \label{th:ex-post}
  $\forall C \ni {\allleadsto}: \nexists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset$.
\end{theorem}
\begin{proof}
  We have, $\forall C \suchthat C \ni {\allleadsto}, \forall θ \subseteq {\allleadsto}$: $θ \subseteq {\allleadsto} \in C$, equivalently, ${\allleadsto} \in S_θ \cap C$, thus $S_θ \cap C ≠ \emptyset$.
\end{proof}
Therefore, synctactic falsifiability guarantees that a claim holds if, and only if, it is not empirically falsifiable.
\begin{theorem}
  \label{th:holdsiff}
  For all syntactically falsifiable $C$: ${\allleadsto} \in C$ iff $\nexists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset$.
\end{theorem}
\begin{proof}
  Consider any syntactically falsifiable $C$.
  By definition of falsifiability, $\forall {\allleadstog}: \nexists θ \subseteq {\allleadstog} \suchthat S_θ \cap C = \emptyset \implies {\allleadstog} \in C$.
  In particular,
  $\nexists θ \subseteq {\allleadsto} \suchthat S_θ \cap C = \emptyset \implies {\allleadsto} \in C$.
  The reverse implication is proven by \cref{th:ex-post}.
\end{proof}

@@

\begin{definition}[Anonymity]
  Given a permutation $\sigma$ over $I$ and any ${\allleadstog} \in P^{I × \allhist}$, let ${\allleadstog} \circ \sigma$ denote $\set{(i, \hist, \phi) \suchthat (\sigma(i), \hist, \phi) \in {\allleadstog}}$ and let $C \circ \sigma$ denote $\set{{\allleadstog} \circ \sigma \suchthat {\allleadstog} \in C}$.
  A claim $C$ is \emph{anonymous} iff $\forall \sigma: C = C \circ \sigma$.
\end{definition}
\begin{example}
  Given $\ar$ and $\phi$, the claim $\ar \ileadstog \phi$ is not anonymous iff $\card{I} ≥ 2$. Indeed, pick any $j ≠ i$ and define $\sigma(i) = j$, $\sigma(j) = i$ and $\forall k \in I \setminus \set{i, j}: \sigma(k) = k$, then $C = \set{{\allleadstog} \suchthat {\allleadstog}(i, \ar) = \phi}$, which contains in particular ${\allleadsto}$ defined as $\forall \hist: [\forall k \in I \setminus \set{j}, {\allleadsto}(k, \hist) = \phi \land {\allleadsto}(j, \hist) = ¬\phi$; while $C \circ \sigma = \set{{\allleadstog} \suchthat {\allleadstog}(j, \ar) = \phi}$ which does not contain ${\allleadsto}$.
\end{example}

@@

Our goal now is to find an exposure protocol $\allleadsto$ with no suitable claim.

\subsection{Ideas for no suitable}
Given $\histk \in \allhist$ and $\ar_l \in \allargs$, let $(\histk, …, \ar_l, ?)$ denote the set
$\set{\histl \suchthat \histk \subset \histl \land \ar_l \in \histlend}$.
Given $\hist \in \allhist$, ${\ileadstog}$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set
$\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
Given $\ar_k, \ar_l \in \allargs$, let
$(…, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?)$ denote the set
$\cup_{\hist \in \allhist} (\hist, \ar_k, ?, \nileadstog \phi, …, \ar_l, ?) =
  \set{\histl \suchthat \exists \hist, \histk \suchthat \hist \subset \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend} =
  \set{\histl \suchthat \exists \histk \suchthat \histk \subset \histl \land \ar_k \in \histkend \land \histk \nileadstog \phi \land \ar_l \in \histlend}$.
Given ${\ileadstog}$, $p \in P$, $s \in \allargs$ and $S \subseteq \allargs$, note that $s \in \ileadstoinvg(p)$ stand for $s \ileadstog p$ and $S \subseteq \ileadstoinvg(p)$ stand for $\forall s \in S: s \ileadstog p$.

\begin{theorem}
  Given any $p \in P, \ar_k, \ar_l \in \allargs$, consider the following claim $C$:
  \begin{multline}
    \label{eq:cl}
    \forall i \in I, \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l},
    \forall \hist \in (…, \ar_1, ?) \cap \nileadstoinvg(p): \\
    (\hist, …, \ar_2, ?) \subseteq \ileadstoinvg(p).
  \end{multline}
  Assume that ${\allleadsto} \in C$. Then
  $\exists i \in I \suchthat [\ar_k \nileadstost p \land \ar_l \nileadstost p]$
  is equivalent to:
  \begin{multline}
    \label{eq:cln}
    \exists i \in I \suchthat \forall \set{\ar_1, \ar_2} \suchthat \set{\ar_1, \ar_2} = \set{\ar_k, \ar_l}:\\
    \exists \hist \in (…, \ar_1, ?) \cap \nileadstoinv(p) \suchthat
    (\hist, …, \ar_2, ?) \subseteq \ileadstoinv(p).
  \end{multline}
\end{theorem}
\begin{proof}
  $\ar_k \nileadstost p$ iff $\exists \hist \suchthat \ar_k \in \histend \land \hist \nileadsto p$.
\end{proof}
\begin{remark}
  Idea.
  That consequence is unfalsifiable so we cannot include anything like this in $C$ (only something stronger, but of course a stronger statement could be false). Therefore, with no addition, we are doomed that exists some situations where no claim is suitable.
\end{remark}
\begin{theorem}
  Pick any $p \in P$ and $\ar_k ≠ \ar_l \in \allargs$ and consider the claim \eqref{eq:cl} and not \eqref{eq:cln}, thus, \eqref{eq:cl} and $\forall i, \ar_k \ileadstostg p \lor \ar_l \ileadstostg p$. It is not falsifiable.
\end{theorem}
\begin{proof}
  %	Intuitively, because it might require (with $\hist = (\ar_1)$) to observe that for a given $i$, $(a_1) \nileadsto p \land (\ar_1, \ar_2) \ileadsto p$ and also $(\ar_2) \nileadsto p \land (\ar_2, \ar_1) \ileadsto p$.
  We need to exhibit some ${\allleadstog} \notin C$ such that $\forall θ \subseteq {\allleadstog}: S_θ \cap C ≠ \emptyset$.
  Define $\allleadstog$ as, $\forall i \in I$, $(\ar_k) \nileadstog p, (\ar_l) \nileadstog p, \forall \hist \in \allhist \setminus \set{(\ar_k), (\ar_l)}: \hist \ileadstog p$.
  It follows that $\ar_k \nileadstostg p \land \ar_l \nileadstostg p$. Thus, ${\allleadstog} \notin C$.
  Now pick any $θ \subseteq {\allleadstog}$.
  % The set $O$ can’t have both $(\ar_k) \nileadstog p$ and $(\ar_l) \nileadstog p$.
